### 2021-11-01 paper/pldi22/formal.tex
Refined formalization

We first define $\ires$ as a specification language to describe JavaScript
semantics.

@@

    \text{Instructions} & \instset &\ni& \inst &::=&
    \refer = \expr \mid
    \varx = \kwcl \kwcr \mid
    \varx = \expr \kwrl \expr^* \kwrr \mid \\&&&&&
    \kwif \; \expr \; \lab \; \lab \mid
    \kwret \; \expr\\

@@

An $\ires$ program $\prog = (\istset, \getfunc, \getinst, \getnext) \in \progset $
consists of initial states and three mappings; $\getfunc: \labset \rightarrow
\funcset$ and $\getinst: \labset \rightarrow \instset$ map labels to their
functions and instructions, respectively, and $\getnext: \labset \rightarrow
\labset$ maps labels to their next labels, where a label $\lab \in \labset$
denotes a program point.  A function $\func \in \funcset$ is defined with its
parameters and body label.  For presentation brevity, we assume that no global
or captured variables exist in this paper.  An instruction $\inst \in \instset$
is an assignment $\refer = \expr$, an object allocation $\varx = \kwcl \kwcr$, a
function call $\varx = \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
\lab \; \lab$, or a return instruction $\kwret \; \expr$.  An invocation of an
abstract algorithm in ECMAScript is compiled to a function call instruction with
a new temporary variable.  We represent loops using branch instructions with
cyclic pointing of labels in $\getnext$.  An expression is a primitive value
$\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A
reference is a variable $\varx$ or an object field $\expr \kwsl \expr \kwsr$.
We write $\expr.\varf$ to briefly represent $\expr \kwsl \code{"f"} \kwsr$.

@@

Since $\ires$ is a specification language for JavaScript, it treats JavaScript
ASTs $\treeset$ as its values. For presentation brevity, we represent a JavaScript
AST as follows:
\[
  \tree ::= \term{\str} \mid \ty_k \langle \tree^* \rangle
\]
A leaf node $\term{\str}$ defined with a string $\str$ denotes a terminal
symbol, and a non-leaf node $\ty_k \langle \tree^* \rangle$ denotes $k$-th
alternative in the syntactic production of nonterminal symbol $\ty$ with its
subtrees $\tree^*$.  The notation $\ty_k.\eval$ denotes an $\ires$ function for
the evaluation of $k$-th alternative in $\ty$, and it takes the AST itself and
its nonterminal subtrees as arguments. If an AST $\tree$ is a subtree of another
AST $\tree'$, we represent it as $\tree \subtree \tree'$.  For example,
Figure~\ref{fig:coalesce-prod} shows a syntactic production for coalesce
expressions.  Consider the following coalesce expression:
\begin{lstlisting}[style=JS]
                    42 ?? true
\end{lstlisting}
Then, the following AST is produced as its parsing result:
\begin{figure}[H]
  \includegraphics[width=.8\columnwidth]{img/ast-example.png}
\end{figure}
\noindent Its evaluation function $\nterm{CoalesceExpression}_0.\eval$ takes
three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and $\tree_2$ in
the figure. Note that $\tree_1$ and $\tree_2$ are subtrees of $\tree_0$ (i.e.,
$\tree_1 \subtree \tree_0$ and $\tree_2 \subtree \tree_0$).

@@

The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset,
\getinst, \getnext)$ is defined as follows:
\[
  \sem{\prog} = \{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}
\]
where $\trans^*$ denotes one or more repetition of $\trans$, and $\st \trans
\st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
\st'$. Now, we define the denotational semantics of expressions, instructions,
and functions.

@@

\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \sem{\varx = \expr}(\st) =
      (\getnext(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
    \]
    where $\sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)$

  \item \underline{Field Assignments}:
    \[
      \sem{\expr_0 \kwsl \expr_1 \kwsr = \expr_2}(\st) =
      (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
        \sem{\expr_2}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
        \obj &=& \heap(\addr) &\wedge\\
        \obj' &=& \obj[\str \mapsto \val]\\
      \end{array}
    \]

  \item \underline{Object Allocations}:
    \[
      \sem{\varx = \kwcl \kwcr}(\st) =
      (\lab, \ctxts, \heap[\addr \mapsto \epsilon], \env[\varx \mapsto
      \addr])
    \]
    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
    \text{Domain}(\heap)$ and $\epsilon$ denotes an empty object.

  \item \underline{Function Calls}:
    \[
      \sem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varp_1, \cdots, \varp_n
        \kwrr \; \lab_\varf) &\wedge\\
        \sem{\expr_j}(\st_{j-1}) &=& (\st_j, \val_j) \;
        [\forall 1 \leq j \leq n] &\wedge\\
        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
        \env' &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n]
        &\wedge\\
        \ctxt &=& (\getnext(\lab), \env, \varx)\\
      \end{array}
    \]

@@

\subsection{Syntactic Views} A syntactic view $\atree \in \atreeset$ is an
augmented JavaScript ASTs with abstract nodes $\treetop$:
\[
  \atree ::= \term{\str} \mid \ty_k \langle \atree^* \rangle \mid \treetop
\]
and its concretization is defined as follows:
\[
  \begin{array}{lcl}
    \gamma(\term{\str}) &=&
    \{ \term{\str} \}\\

    \gamma(\ty_k \langle \atree_1, \cdots, \atree_n \rangle) &=&
    \{ \ty_k \langle \tree_1, \cdots, \tree_n \rangle \mid \tree_j \in
    \gamma(\atree_j) \}\\

    \gamma(\treetop) &=& \treeset\\
  \end{array}
\]
The partial order and join operator between abstract trees are defined as
follows:
\[
  \begin{array}{lcl}
    \atree \order \atree' &\Leftrightarrow& \left\{
      \begin{array}{ll}
        \atree = \atree' &\vee\\

        \atree' = \treetop &\vee\\

        \begin{array}{@{}l@{}}
          \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
          \atree' = \ty_k \langle \atree'_1, \cdots, \atree'_n \rangle \wedge\\
          \forall j. \; \tree_j \order \tree'_j\\
        \end{array}\\
      \end{array}
    \right.\\

    \atree \join \atree' &=& \left\{
      \begin{array}{ll}
        \atree' & \text{if} \; \atree \order \atree'\\

        \atree & \text{if} \; \atree \revorder \atree'\\

        \ty_k \langle \atree''_1, \cdots, \atree''_n \rangle &
        \text{if} \; \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle
        \wedge\\&
        \phantom{\text{if} \;} \atree = \ty_k \langle \atree_1, \cdots, \atree_n
        \rangle \wedge\\&
        \phantom{\text{if} \;} \forall j. \; \atree''_j = \atree_j
        \join \atree'_j\\
        \treetop & \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]
Moreover, we can filter out JavaScript programs using the subtree relation with
syntactic views:
\[
  \atree \subtree \tree' \iff \exists \tree \in \gamma(\atree). \; \tree
  \subtree \tree'
\]

@@

We define a \textit{partial evaluation} $\peval{-}: \progset \rightarrow
\atreeset \rightarrow \progset$ of $\ires$ programs to specialize JavaScript
semantics with a given syntactic view:
\[
  \peval{\prog}(\atree) = \transform(\prog, \asem{\prog}(\atree))
\]
It takes a syntactic view $\atree \in \atreeset$ to restrict arguments of the
corresponding evaluation function. Then, it performs a static analysis
$\asem{-}$ of a given program $\prog$ with the static part $\atree$ and
transforms it using $\transform$ with the analysis result
$\asem{\prog}(\atree)$ to produce a new specialized $\ires$ program.  Now, we
define the static analysis and program transformation of $\ires$ programs and
prove the semantics preservation of the partial evaluation consisting of them.

@@

To define static analysis of $\ires$ programs, we first define abstract domains
of states, calling contexts, environments, and values as follows:
\begin{itemize}
  \item \underline{Abstract States}:
    $\aelemset = \actxtset \times \afsenvset$
    \[
      \begin{array}{lcl}
        \gamma(\afsenv, \actxt) &=& \gamma(\actxt) \cap
        \gamma(\afsenv)\\

        (\actxt, \afsenv) \order (\actxt', \afsenv') &\Leftrightarrow&
        (\actxt \order \actxt') \wedge (\afsenv \order \afsenv')\\

        (\actxt, \afsenv) \join (\actxt', \afsenv') &=&
        (\actxt \join \actxt', \afsenv \join \afsenv')\\

        \bot &=& (\bot, \bot)\\

        \top &=& (\top, \top)\\
      \end{array}
    \]

  \item \underline{Abstract Calling Contexts}:
    $\actxtset = \funcset \finmap \powerset{\labset \times \varset}$
    \[
      \todo
      \begin{array}{lcl}
        \gamma(\actxt) &=& \{ \st \in \stset \mid
          \st = (\lab', (\lab, \_, \varx) :: \_, \_, \_) \wedge \\&&
          \phantom{\{ \st \in \stset \mid} (\lab, \varx) \in
            \actxt(\getfunc(\lab'))
        \}\\

        \actxt \order \actxt' &\Leftrightarrow&
        \forall \func \in \funcset. \; \actxt(\func) \subseteq \actxt'(\func)\\

        \actxt \join \actxt' &=&
        \lambda \func \in \funcset. \; \actxt(\func) \cup \actxt'(\func)\\

        \bot &=& \lambda \func \in \funcset. \; \bot\\

        \top &=& \lambda \func \in \funcset. \; \top\\
      \end{array}
    \]

  \item \underline{Flow-Sensitive Abstract Environments}:
    $\afsenvset = \labset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \gamma(\afsenv) &=& \{ \st \in \stset \mid
          \st = (\lab, \_, \_, \_) \wedge \st \in \gamma(\afsenv(\lab))
        \}\\

@@

        \afsenv \join \afsenv' &=&
        \lambda \lab \in \labset. \; \afsenv(\lab) \join \afsenv'(\lab)\\

        \bot &=& \lambda \lab \in \labset. \; \bot\\

        \top &=& \lambda \lab \in \labset. \; \top\\
      \end{array}
    \]

  \item \underline{Abstract Environments}:
    $\aenvset = \varset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \gamma(\aenv) &=& \{ \st \in \stset \mid
          \forall \varx \in \varset. \;
          \sem{\varx}(\st) \in \gamma(\aenv(\varx))
        \}\\

@@

        \aenv \join \aenv' &=&
        \lambda \varx \in \varset. \;
        \aenv(\varx) \join \aenv'(\varx)\\

        \bot &=& \lambda \varx \in \varset. \; \bot\\

        \top &=& \lambda \varx \in \varset. \; \top\\
      \end{array}
    \]

  \item \underline{Abstract Values}: $\avalset = \valset \uplus \atreeset \uplus
    \{ \bot, \top \}$
    \[
      \begin{array}{lcl}
        \gamma(\aval) &=& \left\{
          \begin{array}{ll}
            \{ \val \} & \text{if} \; \aval = \val\\
            \gamma(\atree) & \text{if} \; \aval = \atree\\
            \varnothing & \text{if} \; \aval = \bot\\
            \valset & \text{if} \; \aval = \top\\
          \end{array}
        \right.\\

        \aval \order \aval' &\Leftrightarrow& \left\{
          \begin{array}{ll}
            \aval = \bot \vee \aval' = \top \vee \aval = \aval' & \vee\\
            \aval = \atree \wedge \aval' = \atree' \wedge
            \atree \order \atree' &\vee\\
            \aval = \tree \wedge \aval' = \atree' \wedge \tree \in
            \gamma(\atree')\\
          \end{array}
        \right.\\

@@

An abstract state $\aelem \in \aelemset$ is a pair of an abstract calling
context and a flow-sensitive abstract environment.  An abstract calling context
$\actxt \in \actxtset$ is a mapping from functions to return labels and
variables in their calling contexts. A flow-sensitive abstract environment
$\afsenv \in \afsenvset$ is a mapping from labels to abstract environments to
represent the shape of environments in each label. An abstract environment
$\aenv \in \aenvset$ is a mapping from variables to abstract values to describe
values stored in variables. An abstract value $\aval \in \avalset$ is a static
value $\val$, a syntactic view $\atree$, a dynamic value $\top$, or nothing
$\bot$. Now, we define abstract semantics of expressions, instructions, and
programs.

@@

\paragraph{Instructions} Then, we define the abstract semantics of instructions
using the abstract semantics of expressions as follows:
\[
  \todo
  \framebox{$\asem{\inst}: \labset \times \aenvset \rightarrow \aelemset
  \rightarrow \aelemset$}
\]
\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \asem{\varx = \expr}(\lab, \aenv) =
      (\bot[\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]], \bot)
    \]
    where $\aval = \asem{\expr}(\aenv)$

  \item \underline{Field Assignments}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr = \expr_2}(\lab, \aenv) =
      (\bot[\getnext(\lab) \mapsto \aenv], \bot)
    \]
  \item \underline{Object Allocations}:
    \[
      \asem{\varx = \kwcl \kwcr}(\lab, \aenv) =
      (\bot[\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]], \bot)
    \]

  \item \underline{Function Calls}:
    \[
      \asem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\lab, \aenv) =
      \text{\todo extensible target functions}
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \aval' = \asem{\expr}(\aenv) &\wedge\\
        (\expr'_j, \_) = \transforme(\expr_j, \aenv) \; [\forall 1 \leq j \leq
        n]\\
      \end{array}
    \]

>>>>

In this section, we introduce a JavaScript semantics specialization with
syntactic views.  We first introduce $\ires$ as a specification language to
describe JavaScript semantics. To provide options to select target semantics, we
also introduce syntactic views as an abstraction of JavaScript ASTs.  Then, we
define a JavaScript semantics specialization with syntactic views as a partial
evaluation of $\ires$ programs, which is a combination of static analysis and
program transformation. Finally, we prove the semantics preservation of the
partial evaluation.

@@

    \text{Instructions} & \instset &\ni& \inst &::=&
    \refer \kweq \expr \mid
    \varx \kweq \kwcl \kwcr \mid
    \varx \kweq \expr \kwrl \expr^* \kwrr \mid \\&&&&&
    \kwif \; \expr \; \lab \; \lab \mid
    \kwret \; \expr\\

@@

An $\ires$ program $\prog = (\istset, \getfunc, \getinst, \getnext) \in \progset $
consists of initial states and three mappings; $\getfunc: \labset \rightarrow
\funcset$ and $\getinst: \labset \rightarrow \instset$ map labels to their
functions and instructions, respectively, and $\getnext: \labset \rightarrow
\labset$ maps labels to their next labels, where a label $\lab \in \labset$
denotes a program point.  A function $\func \in \funcset$ is defined with its
parameters and body label.  For presentation brevity, we assume that no global
or captured variables exist in this paper.  An instruction $\inst \in \instset$
is an assignment $\refer \kweq \expr$, an object allocation $\varx \kweq \kwcl \kwcr$, a
function call $\varx \kweq \expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \;
\lab \; \lab$, or a return instruction $\kwret \; \expr$.  An invocation of an
abstract algorithm in ECMAScript is compiled to a function call instruction with
a new temporary variable.  We represent loops using branch instructions with
cyclic pointing of labels in $\getnext$.  An expression is a primitive value
$\pval$, an operation $\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A
reference is a variable $\varx$ or an object field $\expr \kwsl \expr \kwsr$.
We write $\expr.\varf$ to briefly represent $\expr \kwsl \code{"f"} \kwsr$.

@@

$\ires$ is a specification language for JavaScript that treats JavaScript ASTs
as its values. To handle JavaScript ASTs in $\ires$, we define them with tree
nodes $\nodeset$ as follows:
\[
  \begin{array}{l@{~}c@{~}l@{~}c@{~}l}
    \treeset &\ni& \tree &::=& \ty_k \langle \node^* \rangle\\
    \nodeset &\ni& \node &::=& \str \mid \tree\\
  \end{array}
\]
A JavaScript AST $\ty_k \langle \node_1, \cdots, \node_n \rangle$ denotes $k$-th
alternative in the syntactic production of nonterminal symbol $\ty$ with
multiple tree nodes $\node_1, \cdots, \node_n$.  A tree node is a string for a
terminal symbol or another tree for a nonterminal symbol. We define several
notations to easily deal with JavaScript ASTs.  The notation $\ty_k.\eval$ denotes
an \esalg{Evaluation} function of $k$-th alternative in the production $\ty$.
Similarly, the notation $\tree.\eval$ denotes the \esalg{Evaluation} function of
the AST $\tree$, and it is same with $\ty_k.\eval$ when $\tree = \ty_k \langle
\cdots \rangle$. The \esalg{Evaluation} of each AST takes the AST itself and its
tree nodes that are nonterminals as arguments.  The notation $\getsubs(\tree)$
denotes tree nodes that are subtrees of $\tree$.  For example,
Figure~\ref{fig:coalesce-prod} shows a syntactic production for coalesce
expressions.  Consider the following JavaScript coalesce expression:
\begin{lstlisting}[style=JS]
                    42 ?? true
\end{lstlisting}
Then, the following AST is produced as its parsing result:
\[
  \begin{array}{lcl}
    \tree_0 &=&
    \essyn{CoalesceExpression}_0 \langle \tree_1, \code{"??"}, \tree_2 \rangle\\

    \tree_1 &=&
    \essyn{CoalesceExpressionHead}_1 \langle \tree_3 \rangle\\

    \tree_2 &=&
    \essyn{BitwiseORExpression}_0 \langle \cdots \rangle\\

    \tree_3 &=&
    \essyn{BitwiseORExpression}_0 \langle \cdots \rangle\\
  \end{array}
\]
\begin{figure}[H]
  \includegraphics[width=.8\columnwidth]{img/ast-example.png}
\end{figure}
\noindent Its \esalg{Evaluation} function $\essyn{CoalesceExpression}_0.\eval$
takes three subtrees as arguments annotated by $\tree_0$, $\tree_1$, and
$\tree_2$ in the figure. The ASTs $\tree_0$, $\tree_1$, $\tree_2$, and $\tree_3$
are subtrees of $\tree_0$ (i.e., $\tree_0 \subtree \tree_0, \cdots, \tree_3
\subtree \tree_0$), and $\getsubs(\tree_0) = [\tree_1, \tree_2] \wedge
\getsubs(\tree_1) = [\tree_3]$.

@@

The concrete semantics $\sem{\prog}$ of an $\ires$ program $\prog = (\istset,
\getinst, \getnext)$ is defined as follows:
\[
  \sem{\prog} = \{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}
\]
where $\trans^*$ denotes one or more repetition of $\trans$, and $\st \trans
\st'$ if and only if $\st = (\lab, \_, \_, \_)$ and $\sem{\getinst(\lab)}(\st) =
\st'$. Another way to represent the concrete semantics is to define a transfer
function $\transfer: \powerset{\stset} \rightarrow \powerset{\stset}$:
\[
  \sem{\prog} = \lim_{n \rightarrow \infty}\transfer^n(\istset)
\]
where $\transfer(S) = \{ \st' \mid \st \in S \wedge \st \trans \st' \}$.  Now,
we define the denotational semantics of expressions, instructions, and
functions.

@@

\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \sem{\varx \kweq \expr}(\st) =
      (\getnext(\lab), \ctxts, \heap, \env[\varx \mapsto \val])
    \]
    where $\sem{\expr}(\st) = ((\lab, \ctxts, \heap, \env), \val)$

  \item \underline{Field Assignments}:
    \[
      \sem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\st) =
      (\getnext(\lab), \ctxts, \heap[\addr \mapsto \obj'], \env)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
        \sem{\expr_2}(\st'') &=& ((\lab, \ctxts, \heap, \env), \val) &\wedge\\
        \obj &=& \heap(\addr) &\wedge\\
        \obj' &=& \obj[\str \mapsto \val]\\
      \end{array}
    \]

  \item \underline{Object Allocations}:
    \[
      \sem{\varx \kweq \kwcl \kwcr}(\st) =
      (\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env[\varx \mapsto
      \addr])
    \]
    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
    \text{Domain}(\heap)$

  \item \underline{Function Calls}:
    \[
      \sem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varx_1, \cdots, \varx_n
        \kwrr \; \lab_\varf) &\wedge\\
        \sem{\expr_j}(\st_{j-1}) &=& (\st_j, \val_j) \;
        [\forall 1 \leq j \leq n] &\wedge\\
        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
        \env' &=& [\varx_1 \mapsto \val_1, \cdots, \varx_n \mapsto \val_n]
        &\wedge\\
        \ctxt &=& (\getnext(\lab), \env, \varx)\\
      \end{array}
    \]

@@

\subsection{Syntactic Views}

A syntactic view $\atree \in \atreeset$ is an abstract JavaScript AST with
abstract tree nodes $\anodeset$:
\[
  \begin{array}{l@{~}c@{~}l@{~}c@{~}l}
    \atreeset &\ni& \atree &::=& \ty_k \langle \anode^* \rangle \mid \ty\\
    \anodeset &\ni& \anode &::=& \str \mid \atree\\
  \end{array}
\]
where $\ty$ denotes all ASTs whose nonterminal symbol $\ty$. We define the
concretization of abstract trees $\atreegamma: \atreeset \rightarrow
\powerset{\treeset}$ and that of abstract nodes $\anodegamma: \anodeset
\rightarrow \powerset{\nodeset}$ as follows:
\[
  \begin{array}{lcl}
    \atreegamma(\ty_k \langle \anode_1, \cdots, \anode_n \rangle) &=&
    \{ \ty_k \langle \node_1, \cdots, \node_n \rangle \mid \node_j \in
    \anodegamma(\anode_j) \}\\

    \atreegamma(\ty) &=&
    \{ \tree \in \treeset \mid \tree = \ty_k \langle \cdots \rangle \}\\

    \anodegamma(\str) &=& \{ \str \}\\

    \anodegamma(\atree) &=& \atreegamma(\atree)\\
  \end{array}
\]
% \[
%   \begin{array}{lcl}
%     \anode \order \anode' &\Leftrightarrow& \left\{
%       \begin{array}{ll}
%         \anode = \anode' &\vee\\
% 
%         \anode' = \ty &\vee\\
% 
%         (\anode = \atree \wedge \anode' = \atree' \wedge \atree \order
%         \atree')\\
%       \end{array}
%     \right.\\
% 
%     \atree \order \atree' &\Leftrightarrow& \left\{
%       \begin{array}{ll}
%         \atree = \atree' &\vee\\
% 
%         \atree' = \treetop &\vee\\
% 
%         \begin{array}{@{}l@{}}
%           \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle \wedge
%           \atree' = \ty_k \langle \atree'_1, \cdots, \atree'_n \rangle \wedge\\
%           \forall j. \; \tree_j \order \tree'_j\\
%         \end{array}\\
%       \end{array}
%     \right.\\
% 
%     \atree \join \atree' &=& \left\{
%       \begin{array}{ll}
%         \atree' & \text{if} \; \atree \order \atree'\\
% 
%         \atree & \text{if} \; \atree \revorder \atree'\\
% 
%         \ty_k \langle \atree''_1, \cdots, \atree''_n \rangle &
%         \text{if} \; \atree = \ty_k \langle \atree_1, \cdots, \atree_n \rangle
%         \wedge\\&
%         \phantom{\text{if} \;} \atree = \ty_k \langle \atree_1, \cdots, \atree_n
%         \rangle \wedge\\&
%         \phantom{\text{if} \;} \forall j. \; \atree''_j = \atree_j
%         \join \atree'_j\\
%         \treetop & \text{otherwise}\\
%       \end{array}
%     \right.\\
%   \end{array}
% \]
Moreover, we define abstract subtree relation $\asubtree \subseteq \atreeset
\times \treeset$:
\[
  \atree \; \asubtree \; \tree' \iff \exists \tree \in \atreegamma(\atree). \;
  \tree \subtree \tree'
\]
to filter out JavaScript programs not related to a given syntactic view.
Similar to $\getsubs(\tree)$, an abstract helper function $\agetsubs(\atree)$
denotes abstract tree nodes that are syntactic views when $\atree = \ty_k
\langle \cdots \rangle$.

@@

We define a \textit{partial evaluation} $\peval{-}: \progset \rightarrow
\atreeset \rightarrow \progset$ of $\ires$ programs to specialize JavaScript
semantics with a given syntactic view:
\[
  \peval{\prog}(\atree) = \transform{\prog} \circ \asem{\prog} (\atree)
\]
It takes a syntactic view $\atree \in \atreeset$ to restrict arguments of the
corresponding \esalg{Evaluation} function. Then, it performs a static analysis
$\asem{-}$ of a given program $\prog$ with the syntactic view $\atree$ and
transforms the program using $\transform{-}$ with the analysis result
$\asem{\prog}(\atree)$ to produce a specialized $\ires$ program.  Since the
\esalg{Evaluation} of $\ty$ might one or more $\ires$ functions, we only define
the partial evaluation when $\atree = \ty_k \langle \cdots \rangle$.  Now, we
define the static analysis and program transformation of $\ires$ programs and
prove the semantics preservation of the partial evaluation consisting of them.

@@

The static analysis $\asem{\prog}(\atree)$ performs an abstract
interpretation~\cite{ai1977, ai1992} to abstract concrete semantics under the
given given syntactic view $\atree$.  We first define abstract domains of
states, calling contexts, environments, and values as follows:
\begin{itemize}
  \item \underline{Abstract States}:
    $\aelemset = \amctxtset \times \atctxtset \times \afsenvset$
    \[
      \begin{array}{lcl}
        \aelemgamma(\amctxt, \atctxt, \afsenv) &=&
        \amctxtgamma(\amctxt) \cup
        (\atctxtgamma(\atctxt) \cap \afsenvgamma(\afsenv))\\

        (\amctxt, \atctxt, \afsenv) \order
        (\amctxt', \atctxt', \afsenv') &\Leftrightarrow&
        (\amctxt \order \amctxt') \wedge
        (\atctxt \order \atctxt') \wedge
        (\afsenv \order \afsenv')\\

        (\amctxt, \atctxt, \afsenv) \join (\amctxt', \atctxt', \afsenv') &=&
        (\amctxt \join \amctxt', \atctxt \join \atctxt', \afsenv \join \afsenv')\\
      \end{array}
    \]

  \item \underline{Merged Calling Contexts}:
    $\amctxtset = \powerset{\labset}$
    \[
      \begin{array}{lcl}
        \amctxtgamma(\amctxt) &=& \{ \st \in \stset \mid
          \st = (\lab, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \exists 1 \leq j \leq n. \; \ctxt_j = (\lab_j, \_, \_) \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \lab_j \in \amctxt
        \}\\

        \amctxt \order \amctxt' &\Leftrightarrow&
        \amctxt \subseteq \amctxt\\

        \amctxt \join \amctxt' &=&
        \amctxt \cup \amctxt\\
      \end{array}
    \]

  \item \underline{Target Calling Contexts}:
    $\atctxtset = \powerset{\labset \times \funcset}$
    \[
      \begin{array}{lcl}
        \atctxtgamma(\atctxt) &=& \{ \st \in \stset \mid
          \st = (\lab_0, [\ctxt_1, \cdots, \ctxt_n], \_, \_) \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \forall 1 \leq j \leq n. \; \ctxt_j = (\lab_j, \_, \_) \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \exists 0 \leq m \leq n. \; \getfunc(\lab_m) = \ty_k.\eval \wedge\\&&

          \phantom{\{ \st \in \stset \mid}
          \forall 1 \leq j \leq m. \; (\lab_j, \getfunc{\lab_{j-1}}) \in \atctxt
        \}\\

        \atctxt \order \atctxt' &\Leftrightarrow& \atctxt \subseteq \atctxt\\

        \atctxt \join \atctxt' &=& \atctxt \cup \atctxt'\\
      \end{array}
    \]

  \item \underline{Flow-Sensitive Abstract Environments}:
    $\afsenvset = \labset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \afsenvgamma(\afsenv) &=& \{ \st \in \stset \mid
          \st = (\lab, \_, \_, \_) \wedge \st \in \aenvgamma(\afsenv(\lab))
        \}\\

@@

        \afsenv \join \afsenv' &=&
        \lambda \lab \in \labset. \; \afsenv(\lab) \join \afsenv'(\lab)\\
      \end{array}
    \]

  \item \underline{Abstract Environments}:
    $\aenvset = \varset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \aenvgamma(\aenv) &=& \{ \st \in \stset \mid
          \forall \varx \in \varset. \;
          \sem{\varx}(\st) \in \avalgamma(\aenv(\varx))
        \}\\

@@

        \aenv \join \aenv' &=&
        \lambda \varx \in \varset. \;
        \aenv(\varx) \join \aenv'(\varx)\\
      \end{array}
    \]

  \item \underline{Abstract Values}: $\avalset = \valset \uplus \atreeset \uplus
    \{ \top, \bot,  \}$
    \[
      \begin{array}{lcl}
        \avalgamma(\aval) &=& \left\{
          \begin{array}{ll}
            \{ \val \} & \text{if} \; \aval = \val\\
            \atreegamma(\atree) & \text{if} \; \aval = \atree\\
            \valset & \text{if} \; \aval = \top\\
            \varnothing & \text{if} \; \aval = \bot\\
          \end{array}
        \right.\\

        \aval \order \aval' &\Leftrightarrow& \left\{
          \begin{array}{ll}
            \aval = \bot \vee \aval' = \top \vee \aval = \aval' & \vee\\
            \aval = \atree \wedge \aval' = \atree' \wedge
            \atree \order \atree' &\vee\\
            \aval = \tree \wedge \aval' = \atree' \wedge \tree \in
            \atreegamma(\atree')\\
          \end{array}
        \right.\\

@@

An abstract state $\aelem \in \aelemset$ is a triple of a merged and target call
edges and a flow-sensitive abstract environment.  A merged calling context
$\amctxt \in \amctxtset$ is a set of call labels representing merged function
calls. A target calling context $\atctxt \in \atctxtset$ is a set of possible
static call edges from labels to function, and it represents the scope of static
analysis. To more precisely represent states in target calling contexts, we
define a flow-sensitive abstract environment $\afsenv \in \afsenvset$. It is
a mapping from labels to abstract environments to represents the shape of
environments in each label. An abstract environment $\aenv \in \aenvset$ is a
mapping from variables to abstract values to describe values stored in
variables. An abstract value $\aval \in \avalset$ is a static value $\val$, a
syntactic view $\atree$, a dynamic value $\top$, or nothing $\bot$.  Now, we
define abstract semantics of expressions, instructions, and programs.

@@

\paragraph{Instructions} Then, we define the abstract semantics of instructions
as follows:
\[
  \framebox{$\asem{\inst}: \amctxtset \times \atctxtset \times \labset \times
    \aenvset \rightarrow
  \aelemset$}
\]
\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \asem{\varx \kweq \expr}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \aval]])
    \]
    where $\aval = \asem{\expr}(\aenv)$

  \item \underline{Field Assignments}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr \kweq \expr_2}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv])
    \]

  \item \underline{Object Allocations}:
    \[
      \asem{\varx \kweq \kwcl \kwcr}(\amctxt, \atctxt, \lab, \aenv) =
      (\amctxt, \atctxt, [\getnext(\lab) \mapsto \aenv[\varx \mapsto \top]])
    \]

  \item \underline{Function Calls}:
    \[
      \asem{\varx \kweq \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\amctxt,
      \atctxt, \lab, \aenv) = (\amctxt', \atctxt', \afsenv)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \aval &=& \asem{\expr}(\aenv) &\wedge\\
        \aval_j &=& \asem{\expr_j}(\aenv) \; [\forall 1 \leq j \leq n] &\wedge\\
        (\amctxt', \atctxt') &=& \left\{
          \begin{array}{ll}
            (\amctxt, \atctxt \cup \{ (\lab, \func) \} &
            \text{if} \; \aval = \func \wedge \exists j. \; \aval_j \neq \top\\
